\newcommand{\arxiv}[1]
  {\href{https://arxiv.org/abs/#1}{\texttt{arXiv:#1}}}


\section*{Selected Papers}
\begin{cvcontent}
 \begin{enumerate}[label={[\arabic*]}, leftmargin=1cm]
    %
    \item \label{item:lamarr-ichep} L. Anderlini \emph{et al.},
    \emph{Lamarr: the ultra-fast simulation option for the LHCb experiment},
    in \emph{41st International Conference on High Energy Physics -- PoS(ICHEP2022)},
    \href{https://doi.org/10.22323/1.414.0233}{\textbf{414} 233, 2022}
    %
%    \item \label{item:lamarr-acat} L. Anderlini \emph{et al.},
%    \emph{Lamarr: LHCb Ultra-Fast Simulation based on machine learning models deployed within Gauss},
%    in \emph{21st International Workshop on Advanced Computing and Analysis Techniques in Physics Research},
%    in preparation for \href{https://iopscience.iop.org/journal/1742-6596}{J. Phys. Conf.}
    %
    \item \label{item:gan-pm} F. Ratnikov \emph{et al.},
    \emph{A full detector description using neural network driven simulation},
    in \emph{15th Pisa Meeting on Advanced Detectors},
    \href{https://doi.org/10.1016/j.nima.2022.167591}{Nucl. Instrum. Meth. A \textbf{1046} (2023) 167591}
    %
    \sloppy
    \item \label{item:gan-acat} L. Anderlini \emph{et al.},
    \emph{Towards Reliable Neural Generative Modeling of Detectors},
    in \emph{20th International Workshop on Advanced Computing and Analysis Techniques in Physics Research},
    \arxiv{2204.09947}
    %
    \item \label{item:hopaas} M. Barbetti and L. Anderlini,
    \emph{Hyperparameter Optimization as a Service on INFN Cloud},
    in \emph{21st International Workshop on Advanced Computing and Analysis Techniques in Physics Research},
    in preparation for \href{https://iopscience.iop.org/journal/1742-6596}{J. Phys. Conf.}
    %
    \item \label{item:scikinc} L. Anderlini and M. Barbetti, 
    \emph{scikinC: a tool for deploying machine learning as binaries}, 
    in \emph{Computational Tools for High Energy Physics and Cosmology -- PoS(CompTools2021)}, 
    \href{https://doi.org/10.22323/1.409.0034}{\textbf{409} 034, 2022}
    %
    \item \label{item:phys-med} E. M. Abenavoli \emph{et al.},
    \emph{Characterization of mediastinal bulky lymphomas with FDG-PET-based radiomics and machine learning techniques},
    in preparation for \href{https://www.mdpi.com/journal/cancers}{Cancers}
    %
    \item \label{item:smog-pub} LHCb Collaboration,
    \emph{Measurement of antiproton production from antihyperon decays in pHe collisions at $\sqrt{s_{\rm{NN}}}=110~\rm{GeV}$},
    \arxiv{2205.09009}
    %
 \end{enumerate}
\end{cvcontent}