\section*{Research Activities}
\begin{cvcontent}
  Since 2019, I am member of the LHCb experiment at CERN's Large 
  Hadron Collider (LHC). In this context, I had the opportunity to 
  focus on some of the most challenging computing developments for 
  the next-generation High Energy Physics experiments, including the 
  application of advanced \emph{Deep Learning} techniques to large 
  samples of proton-proton collision data and their training and 
  deployment in a world-wide distributed environment.
%  \\
  In the same period, in collaboration with the Careggi University 
  Hospital in Florence, 
  I also had the opportunity to contribute to the research in Medical 
  Physics by applying \emph{Machine Learning} techniques to unpublished 
  radiomic\footnote{In the field of medicine, \emph{Radiomics} is a new 
  field of image analysis in which digital medical images are converted 
  into quantitative high-dimensional data.} datasets.
%  \\
  I am currently preparing my Ph.D. thesis in Smart Computing at 
  the University of Florence with original contributions on 
  LHCb Simulation and Radiomics.
  \\ [1.5mm]
  My research activity is mainly devoted to the development of a novel 
  LHCb \emph{ultra-fast simulation} framework, called \textsc{Lamarr}
  \ref{pub:lamarr-ichep} that I have recently presented during the 
  international workshop \hyperlink{acat-2022}{[ACAT22]}. \textsc{Lamarr} 
  consists of a pipeline of modular parameterizations designed to replace 
  both the physics simulation and the reconstruction steps. Most of the 
  parameterizations rely on Machine Learning algorithms \ref{pub:gan-pm},
  such as \emph{generative models}, that were demonstrated to be 
  able to well reproduce the distributions obtained from the 
  detailed simulation \ref{pub:gan-acat}.
  \\ [1.5mm]
  I am an active developer within the LHCb Simulation team, with
  the responsibility for the parameterization of the LHCb Particle 
  Identification (PID) system. Generative Deep Neural Networks
  succeed in reproducing the analysis-level classifiers defined 
  by the PID reconstruction algorithms, showing promising results
  already presented at national [\hyperlink{ccr-2021}{CCR21}, 
  \hyperlink{sif-2021}{SIF21}] and international \hyperlink{ltd}{[LTD]} 
  conferences. Parameterizing with high accuracy the PID multivariate 
  distributions requires training such specialized models
  in GPU-intensive \emph{hyperparameter optimization} campaigns.
%  \\
  To profit from multiple computing resources made opportunistically
  available to the LHCb Collaboration, I proposed a client-server
  approach with a centralized service defining the optimization
  procedure in multiple instances running in parallel on different 
  providers. The approach was validated on resources made available 
  to LHCb by CERN via the \hyperlink{cloud-bank}{[CloudBank]} initiative
  or by INFN and CINECA granting access to the Marconi 100 supercomputer. 
  During the last few months, I have been converting the validated 
  prototype into an INFN Cloud service, named Hopaas \ref{pub:hopaas}, 
  featuring a web dashboard and a token-based user authentication 
  procedure integrated to the INFN user identity management tools.
  I have recently presented Hopaas during the international workshop 
  \hyperlink{acat-2022}{[ACAT22]}.
  \\ [1.5mm]
  To enable the deployment of the optimized models in the LHCb software 
  stack, running in multiple data centers around the world connected 
  via the LHCb Computing Grid, I contributed to the development of 
  \texttt{scikinC} \ref{pub:scikinc}, a tool able to translate 
  Machine Learning models into C files that, once compiled, 
  are distributed with the CernVM File System and dynamically 
  linked to the LHCb applications.
  \\ [1.5mm]
  My research is strongly connected to the data analysis effort within 
  the LHCb group in Florence, exploiting advanced statistical treatment 
  of the PID classifiers with Machine Learning techniques to shed light 
  on the nature and the antiprotons observed in primary cosmic rays 
  \ref{pub:smog-pub}.
  \\ [1.5mm]
  As part of the research activities for my Ph.D., I am exploring the 
  application of Machine Learning techniques to Medical Physics to 
  develop solutions employable in the emerging ``personalized medicine''. 
  In particular, I am working to build a Machine Learning model able 
  to infer the histological type of mediastinal bulky lymphomas, one 
  of the most common hematologic cancers, only using radiomic features 
  drawn from PET images \ref{pub:phys-med}. The aim of the study is to 
  understand how PET radiomic features may predict lymphoma histology 
  and in the future support its diagnosis, offering non-invasive solutions 
  tailored to the single patient. Preliminary results are promising and
  have been presented at national \hyperlink{sif-2022}{[SIF22]} and 
  international \hyperlink{ecmp-2022}{[ECMP2022]} conferences.
  \\ [1.5mm]
  In 2020 I joined the \emph{ML-INFN} project, a national initiative 
  of INFN to coordinate the effort toward the widespread application 
  of Machine Learning technologies to research activities. In 2022 I 
  helped in organizing the Third ML-INFN Hackathon for which I gave
  two lectures, one about deep generative models and the other about
  Bayesian hyperparameter optimization \hyperlink{mlinfn-2022}{[ML\_INFN22]}.
\end{cvcontent}