\section*{About Me}
\begin{cvcontent}
I am a Ph.D. student in Smart Computing at the University of Florence since November 2020. After a Master degree in Particle Physics, I deal with \emph{Artificial Intelligence} developing possible applications to Medical Physics, Nuclear Physics and Particle Physics. I am associated with the National Institute for Nuclear Physics (INFN) and member of the LHCb Collaboration.
\\ [2mm]
In September 2017 I discussed a Bachelor Thesis focused on Data Analysis work in High Energy Physics: the study of the decays of \textit{charmonium} states into purely hadronic final states as reconstructed with the LHCb experiment at CERN. A scholarship funded by the University of Florence offered me the opportunity of carrying out part of the activities at CERN.
\\ [2mm]
In June 2020 I discussed a Master Thesis focused on the development of a Python-based simulation framework for Particle Physics applications integrated with Deep Learning solutions to parameterize the detector response of the LHCb experiment. A fellowship funded by INFN has offered me the opportunity of passing three months at CERN, and forging new relationships within a stimulant and international environment.
\\ [2mm]
I am member of AISF, the Italian Association of Physics Students, which promotes and stimulates expanding the professional networks of its members in a national and international context. I held the position of President of the Florence Local Committee until May 2019; now I am the National Secretary and Vice President of AISF.
\end{cvcontent}